---
title: "biocSubmitted: analyze repository content for packages submitted to Bioconductor"
shorttitle: "outlier dytection methods"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{biocSubmitted: LLM-based analysis of repository content for R packages}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

This package is intended to be part of a workflow that summarizes packages
submitted to Bioconductor.  This code assumes that `GITHUB_TOKEN` and
a suitable LLM API token (default expectation is `ANTHROPIC_API_KEY`) is available to 
`Sys.getenv`.

Illustration:

- Get existing open issues

```{r lk1, message=FALSE}
library(biocSubmitted)
alliss = get_issues()
```

- Extract repository URLs

```{r lk2}
allu = vapply(alliss, function(x) extract_repo_from_body(x$body), character(1))
head(allu)
```

- Analyze content for a repository.  This uses a function `vig2data` with specific
prompts and suggestions for summarization.

```{r lk3}
analyze_repo_vignette(allu[1])
```
